Appendix 2: Simulating 20-species landscapes

### 2016-03-15 Harris_2015/manuscript-materials/draft.tex
as resubmitted to Ecology

\hyperdef{}{ref-harrisux5festimatingux5f2016}{\label{ref-harrisux5festimatingux5f2016}}
Harris, D. J. 2016. Estimating species interactions in large,
abiotically structured communities using markov networks and stochastic
approximation. bioRxiv.

@@

\hyperdef{}{ref-xiaoux5fstrongux5f2015}{\label{ref-xiaoux5fstrongux5f2015}}
Xiao, X., D. J. McGlinn, and E. P. White. 2015. A strong test of the
maximum entropy theory of ecology. The American Naturalist 185:E70--E80.
\end{flushleft}
\end{spacing}

>>>>

\hyperdef{}{ref-harrisux5festimatingux5f2016}{\label{ref-harrisux5festimatingux5f2016}}
Harris, D. J. 2016. Estimating species interactions in large,
abiotically structured communities with markov networks and stochastic
approximation. \emph{in} Multi-process statistical modeling of species'
joint distributions. Figshare.
http://doi.org/10.6084/m9.figshare.3114226.v1.

@@

\hyperdef{}{ref-xiaoux5fstrongux5f2015}{\label{ref-xiaoux5fstrongux5f2015}}
Xiao, X., D. J. McGlinn, and E. P. White. 2015. A strong test of the
maximum entropy theory of ecology. The American Naturalist 185:E70--E80.

\setlength{\parindent}{0em} \setlength{\leftskip}{0em}

\textbf{Figure Captions}

\end{flushleft}
\end{spacing}
